stats-project

### 2020-12-07 R - Deliverable/MSDS 6371 - Project.Rmd
add knit code

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)
library(scales)
library(caret)

# options
#options(scipen = 999)
```

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood )
data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
data_train$GrLivArea2 = data_train$GrLivArea^2
data_test$GrLivArea2 = data_test$GrLivArea^2
summary(data_train)
summary(data_test)

@@

write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")

nrow(stepwise_submission)
sum(is.na(stepwise_submission))
stepwise_submission_na <- stepwise_submission %>% filter_all(any_vars(is.na(.))) 
stepwise_submission_na
```

@@

fw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=fw_predictions)
fw_submission
write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")

nrow(fw_submission)
sum(is.na(fw_submission))
fw_submission_na <- fw_submission %>% filter_all(any_vars(is.na(.))) 
fw_submission_na
```

@@

```{r}
# outliers list
 outliers_forward = c(4, 54,   59,   66,   67,   70,   94,  119,  121,  138,  152,  154,  164,  179,  186,  209,  219,  239,  250,  252,  262,  305,  314,  321,  322,  331,  336,  337,  349,  350,  363,  384,  385,  401,  427,  439,  441,  474,  478,  497,  524,  528,  530,  560,  567,  569,  582,  584,
586,  589,  592,  598,  608,  622,  633,  636,  641,  643,  656,  662,  665,  682,  686,  689,  692,  703,  713,  725,  745,  770,  775,  779,  799,  804,  811,  813,  823,  826,  841,  876,  878,  886,  898,  899,  926,  940,  962,  971, 1018, 1025, 1032, 1045, 1047, 1049, 1063, 1066,
1069, 1128, 1143, 1156, 1169, 1170, 1174, 1176, 1182, 1183, 1217, 1268, 1269, 1285, 1299, 1311, 1323, 1325, 1327, 1329, 1360, 1387, 1389, 1397, 1416, 1424, 1441)

@@

one_encode_custom_train_data
```

@@

custom_fit = ols_step_forward_p(lm_fit_custom, penter=0.05, details = F)
custom_fit
```

```{r}
custom_model = custom_fit$model
ols_press(custom_model)
formatC(ols_press(custom_model), format = "e", digits = 6)
summary(custom_model)
confint(custom_model)
```

@@

custom_predictions = c(predict(custom_model, newdata = one_encode_custom_test_data))
custom_predictions

custom_submission = data.frame(Id= one_encode_custom_test_data$Id, SalePrice=custom_predictions)
custom_submission
write_csv(custom_submission, "../kaggleData/customSelection1Predictions.csv")
```

@@

one_encode_custom_train_data_model2 = one_encode_custom_train_data
one_encode_custom_train_data_model2 =  one_encode_custom_train_data %>% mutate( index=row_number())

custom_model_1_outliers = c(4,    6,   13,   28,   30,   55,   96,  106,  107,  135,  143,  157,  163,  183,  208,  215,  296,  302,  304,  347,  354,  357,  375,  384,  385,  387,  415,  421,  426,  434,  437,  443,  444,  464,  498,  504,  520,  525,  556,  587,  600,  603,  616,  618,  628,  636,  641,  652,
 661,  671,  679,  697,  736,  751,  770,  786,  813,  842,  877,  886,  887,  900,  903,  932,  941,  946,  950,  952,  976, 1001, 1004, 1030, 1033, 1047, 1058, 1064, 1065, 1069, 1079, 1117, 1120, 1124, 1133, 1137, 1138, 1144, 1147, 1173, 1204, 1229, 1234, 1240, 1245, 1265, 1267, 1270,
1277, 1284, 1311)

one_encode_custom_train_data_model2 = one_encode_custom_train_data_model2[!(one_encode_custom_train_data_model2$index %in% custom_model_1_outliers), ]
one_encode_custom_train_data_model2

#get original data again without all the outliers. This way we can scale it using only the values we will utilize, we do this to avoid data leaking
final_one_encode_custom_train_data_model2 = data_train[(data_train$Id %in% one_encode_custom_train_data_model2$Id), ]
final_one_encode_custom_train_data_model2
```
```{r}
# do all the data preprossesing again

final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>% select(Id, selected_features_q2,  SalePrice)

# 2.5Fin does not exist in test data so changing it to 1.5Unf
final_one_encode_custom_train_data_model2$HouseStyle = as.character(final_one_encode_custom_train_data_model2$HouseStyle)
final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))

>>>>

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)
library(scales)
library(caret)
library(dataPreparation)
library(regclass)
# options
#options(scipen = 999)
```

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood )
data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
data_train$GrLivArea2 = data_train$GrLivArea^2
data_test$GrLivArea2 = data_test$GrLivArea^2
dim(data_train)
dim(data_test)

```{r}
 # In this function we will handle missing values ffor numerical and factor columns 
impute_missing_values_func = function(data){

  # create list of  Numerical Columns names
    nums_col = data %>% purrr::discard(~!is.numeric(.)) %>% names

    # create list of  factor Columns names
    char_col = data %>% purrr::discard(~!is.character(.)) %>% names

    # Create a new dataframe for q2 train data, this is a copy of the original train DF
    treated_data = data

    # Input NA's in numerical columns with the mediam value per column
    for (i in nums_col){
     treated_data = treated_data %>% mutate_at(vars(UQ(as.name(i))),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
    }

    # Create a new factor level called None for each NA in factor columns
    for (i in char_col){
      treated_data[i][is.na(treated_data[i])] = "None"
    }

    return(treated_data)

}

show_missing_values = function(data){
      missing.values <- data %>%
        gather(key = "key", value = "val") %>%
        mutate(is.missing = is.na(val)) %>%
        group_by(key, is.missing) %>%
        summarise(num.missing = n()) %>%
        filter(is.missing==T) %>%
        select(-is.missing) %>%
        arrange(desc(num.missing))

    print(missing.values$key)

}

```{r message=FALSE, warning=FALSE}
# Let's handle the missing values
# show missing values on train DF

#show_missing_values(data_train)
#show_missing_values(data_test)
#data_train_q2 = impute_missing_values_func(data_train)
#data_test_q2 = impute_missing_values_func(data_test)

# show missing values on treated train DF - there should be 0
#show_missing_values(data_train_q2)
#show_missing_values(data_test_q2)

#encoding = build_encoding(data_set = data_train_q2, cols = "auto", verbose = TRUE)
#enconded_data_train_q2 = one_hot_encoder(data_set = data_train_q2, encoding = encoding, drop = TRUE, verbose = F)
#enconded_data_test_q2 = one_hot_encoder(data_set = data_test_q2, encoding = encoding, drop = TRUE, verbose = F)
#print(dim(enconded_data_train_q2))
#print(dim(enconded_data_test_q2))

@@

#write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")

nrow(stepwise_submission)
sum(is.na(stepwise_submission))
stepwise_submission_na <- stepwise_submission %>% filter_all(any_vars(is.na(.))) 
#stepwise_submission_na
```
```{r}
step_wise_vif = VIF(stepwise_model)
step_wise_vif
```

@@

fw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=fw_predictions)
fw_submission
#write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")

nrow(fw_submission)
sum(is.na(fw_submission))
fw_submission_na <- fw_submission %>% filter_all(any_vars(is.na(.))) 
#fw_submission_na
```
```{r}
fw_vif = VIF(fw_model)
c(fw_vif)

@@

```{r}
# outliers list
outliers_forward = c(4, 54,   59,   66,   67,   70,   94,  119,  121,  138,  152,  154,  164,  179,  186,  209,  219,  239,  250,  252,  262,  305,  314,  321,  322,  331,  336,  337,  349,  350,  363,  384,  385,  401,  427,  439,  441,  474,  478,  497,  524,  528,  530,  560,  567,  569,  582,  584,
 586,  589,  592,  598,  608,  622,  633,  636,  641,  643,  656,  662,  665,  682,  686,  689,  692,  703,  713,  725,  745,  770,  775,  779,  799,  804,  811,  813,  823,  826,  841,  876,  878,  886,  898,  899,  926,  940,  962,  971, 1018, 1025, 1032, 1045, 1047, 1049, 1063, 1066,
 1069, 1128, 1143, 1156, 1169, 1170, 1174, 1176, 1182, 1183, 1217, 1268, 1269, 1285, 1299, 1311, 1323, 1325, 1327, 1329, 1360, 1387, 1389, 1397, 1416, 1424, 1441)
#outliers_forward = c(1047,770,1047,1424)

@@

custom_train_data_outliers = data_train[(data_train$Id %in% outliers_forward), ]
#custom_train_data_outliers
hist(custom_train_data_outliers$SalePrice)
hist(one_encode_custom_train_data$SalePrice)
```

@@

custom_fit = ols_step_forward_p(lm_fit_custom, penter=0.05, details = F)
custom_fit
```
```{r}
outliers_forward

```
```{r}
custom_model = custom_fit$model
ols_press(custom_model)
formatC(ols_press(custom_model), format = "e", digits = 6)
summary(custom_model)
#confint(custom_model)
```

@@

custom_predictions = c(predict(custom_model, newdata = one_encode_custom_test_data))
#custom_predictions

custom_submission = data.frame(Id= one_encode_custom_test_data$Id, SalePrice=custom_predictions)
#custom_submission
#write_csv(custom_submission, "../kaggleData/customSelection3Predictions.csv")
```

@@

custom1_vif = VIF(custom_model)
c(custom1_vif)
```

```{r}
#one_encode_custom_train_data_model2

```{r}
one_encode_custom_train_data_model2 = one_encode_custom_train_data

one_encode_custom_train_data_model2$index = seq.int(nrow(one_encode_custom_train_data_model2))
#one_encode_custom_train_data_model2

 custom_model_1_outliers = c( 556)
#
#
#
 one_encode_custom_train_data_model2 = one_encode_custom_train_data_model2[!(one_encode_custom_train_data_model2$index %in% custom_model_1_outliers), ]

 # one_encode_custom_train_data_model2
#
#
#get original data again without all the outliers. This way we can scale it using only the values we will utilize, we do this to avoid data leaking
 final_one_encode_custom_train_data_model2 = data_train[(data_train$Id %in% one_encode_custom_train_data_model2$Id), ]
 #final_one_encode_custom_train_data_model2
```

```{r}
# do all the data preprossesing again
final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>% select(Id, selected_features_q2,  SalePrice)

# # 2.5Fin does not exist in test data so changing it to 1.5Unf
final_one_encode_custom_train_data_model2$HouseStyle = as.character(final_one_encode_custom_train_data_model2$HouseStyle)
final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))
